Demes: a standard format for demographic models

### 2022-08-26 paper.tex
Add Data availability section as requested
New sections for funding and conlict of interest

\section*{Acknowledgments}
We would like to thank the editor and reviewers for helpful
comments that have significantly improved this manuscript.
Graham Gower was supported by a Villum Fonden Young Investigator award to Fernando Racimo (project no. 00025300).
Ryan Gutenkunst and Travis Struck were supported by the National Institute of General Medical Sciences of the National Institutes of Health (R01GM127348 to RNG).
Matthew Hartfield is supported by a NERC Independent Research Fellowship (NE/R015686/1).
Jerome Kelleher is supported by the Robertson Foundation.
Stephan Schiffels was supported by funding from the European Research Council (ERC) under the European Union’s Horizon 2020 research and innovation programme (grant agreement No 851511).
Gertjan Bisschop was supported by funding from the ERC(ModelGenomLand, 757648).

>>>>

\section*{Data Availability}
The Demes specification and documentation are available at
\url{https://popsim-consortium.github.io/demes-spec-docs/}

\section*{Acknowledgments}
We would like to thank the editor and reviewers for helpful
comments that have significantly improved this manuscript.

\section*{Funding}
Graham Gower was supported by a Villum Fonden Young Investigator award to Fernando Racimo (project no. 00025300).
Ryan Gutenkunst and Travis Struck were supported by the National Institute of General Medical Sciences of the National Institutes of Health (R01GM127348 to RNG).
Matthew Hartfield was supported by a NERC Independent Research Fellowship (NE/R015686/1).
Jerome Kelleher was supported by the Robertson Foundation.
Stephan Schiffels was supported by funding from the European Research Council (ERC) under the European Union’s Horizon 2020 research and innovation programme (grant agreement No 851511).
Gertjan Bisschop was supported by funding from the ERC(ModelGenomLand, 757648).

\section*{Conflicts of interest}
The authors declare that there is no conflict of interest.
